%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------
\cvsection{Coop Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------
\cventry
{Embedded Software Engineering} % Job title
{Smartwave Technologies} % Organization
{Toronto, CA} % Location
{Aug. - Dec. 2019} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {
    Designed a custom advertising format allowing
    various products to communicate under the 
    \textbf{Bluetooth 5} standard using only the advertising channel
    reducing battery consumption 
}
\item {
    Implemented a firmware targeting
    \textbf{Scilicon Labs Bluetooth Low Energy Series}
    to send data in periodic, burst and random patterns
}
\item {
    Refactored and modularized the company's code base 
    into libraries reducing code size by 30\%
}
\end{cvitems}
}

%------------------------------------------------
\cventry
{FPGA Crypto Developer} % Job title
{Envieta System LLC} % Organization
{Maryland, US} % Location
{Aug. - Dec. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {
    Implemented a post-quantum cryptosystem - 
    \textbf{\href{https://pq-crystals.org/}{CRYSTALS-Kyber}} 
    on \textbf{FPGA} board using \textbf{VHDL} allowing
    future-proof security standard to increase product value
}
\item {
    Verified the implementation on 
    \textbf{DE10-Nano board} running drivers 
    written in C to ensure run-time requirements 
    and security standards
}
\item {
    Incoporated the usage of multi-port memory allowing 
    a \textbf{4x speed up} on the system’s critical path
}
\end{cvitems}
}

%------------------------------------------------    
\cventry
{Android Developer} % Job title
{Sensibill Inc.} % Organization
{Toronto, CA} % Location
{Jan. - Apr. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {
    Integrated a smoother UI experience allowing 
    the user to capture longer receipts by using 
    \textbf{shape and contour detection} in \textbf{OpenCV}, 
    resulting in better image quality 
    and higher accuracy data extraction from
    the receipt
}
\item {
    Redesigned receipt capture function 
    using \textbf{Kotlin} from scratch 
    for higher readability and cleaner architecture
}
\end{cvitems}
}

%------------------------------------------------
\cventry
{Mobile Development Engineering} % Job title
{Ritual Technologies Inc.} % Organization
{Toronto, CA} % Location
{May. - Aug. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {
    Accomplished smooth transition to 
    \textbf{Android Oreo} 
    by restructuring notifications using 
    \textbf{Notification Channels}
    and adding 
    \textbf{AutoFill} onto the sign-in flow
}
\item {
    Added easy-switching between testing servers 
    to visualize in-progress features 
    in the compiled application, 
    resulting in 30\% shorter development time for new features
}
\end{cvitems} 
}

%------------------------------------------------
% \cventry
% {Test Engineering} % Job title
% {Ritual Technologies Inc.} % Organization
% {Toronto, CA} % Location
% {Aug. - Dec. 2016} % Date(s)
% { % Description(s) of tasks/responsibilities
% \begin{cvitems}
% \item {
%     Engineered a chrome extension automating 
%     ticket dispute report process with Stripe. Inc, 
%     reducing operations time by 70\%
% }
% \end{cvitems}
% }

%------------------------------------------------
\end{cventries}