%----------------------------------------------------------------------------------------
%	SECTION TITLE
%----------------------------------------------------------------------------------------

\cvsection{Work Experience}

%----------------------------------------------------------------------------------------
%	SECTION CONTENT
%----------------------------------------------------------------------------------------

\begin{cventries}

%------------------------------------------------

\cventry
{FPGA Crypto Developer} % Job title
{Envieta System LLC} % Organization
{Maryland, US} % Location
{Aug. - Dec. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Implemented a post-quantum cryptosystem - CRYSTALS-Kyber on FPGA board using VHDL allowing
future-proof security standard to increase product value}
\item {Verified the implementation on DE10-Nano board with the SoC Linux system running custom C drivers
to assure it fulfills run-time requirements and security standards}
\item {Piloted the usage of multi-port memory allowing a 4x speed up on the system’s critical path}
\end{cvitems}
}

%------------------------------------------------    

\cventry
{Android Developer} % Job title
{Sensibill Inc.} % Organization
{Toronto, CA} % Location
{Jan. - Apr. 2018} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Integrated a smoother UI experience allowing the user to capture longer receipts by using shape and
contour detection in OpenCV, resulting in better image quality and more accurate data extraction from
the receipt}
\item {Redesigned receipt capture function using Kotlin from scratch for higher readability and cleaner code}
\end{cvitems}
}

%------------------------------------------------

\cventry
{Mobile Development Engineering} % Job title
{Ritual Technologies Inc.} % Organization
{Toronto, CA} % Location
{May. - Aug. 2017} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Accomplished smooth transition to Android Oreo by restructuring notifications using Notification
Channels and adding AutoFill onto the sign-in flow}
\item {Designed in-app add-ons allowing switching between testing server to visualize in-progress features in
the compiled application, resulting in 30\% shorter development time of new features}
\end{cvitems} 
}

%------------------------------------------------

\cventry
{Test Engineering} % Job title
{Ritual Technologies Inc.} % Organization
{Toronto, CA} % Location
{Aug. - Dec. 2016} % Date(s)
{ % Description(s) of tasks/responsibilities
\begin{cvitems}
\item {Engineered a chrome extension automating ticket dispute report process with Stripe. Inc, reducing
operations time by 70\%}
\end{cvitems}
}

%------------------------------------------------

\end{cventries}